Using an iterated block particle filter via \pkg{spatPomp}

### 2024-08-05 ms.Rnw
some updates

%%%%%% iiiiiiii %%%%
<<bm-model,echo=T,eval=T>>=
library(spatPomp)
i <- 2
b <- bm2(U=4,N=switch(i,10,200),unit_specific_names="rho")
plot(b)
@

<<bm-followup,echo=F,eval=T>>=
U <- length(unit_names(b))
@

@@

<<model-he10-g,eval=T,echo=F>>=
stew(file=paste0(m_dir,"m-g-sim.rda"),{
he10_model <- he10(U=4,dt=1/365,Tmax=switch(i,1955,1964),
  expandedParNames=c("g"),
  towns_selected=c(1,2,11,12),
  basic_params = c(
    alpha =0.99,      iota=0,          R0=30,
    cohort=0.5,  amplitude=0.3,     gamma=52,
    sigma=52,           mu=0.02,  sigmaSE=0.05,
    rho=0.5,           psi=0.1,         g=800,
    S_0=0.036,         E_0=0.00007,   I_0=0.00006
  )
)
m_g <- simulate(he10_model,seed=27)
if(dim(obs(m_g))!=dim(obs(m_R0)) || any(obs(m_g)-obs(m_R0) != 0)) stop("m_g and m_R0 should have the same synthetic data")
})
@

>>>>

%%%%%% iiiiiiii %%%%
<<bm-model,echo=T,eval=T>>=
library(spatPomp)
i <- 1
b <- bm2(U=4,N=switch(i,10,200),unit_specific_names="rho")
plot(b)
@

<<bm-followup,echo=F,eval=T>>=
if(i==1) cores <- 2   # no need to use all available cores when i=1
U <- length(unit_names(b))
@

@@

<<model-he10-g,eval=T,echo=F>>=
stew(file=paste0(m_dir,"m-g-sim.rda"),{
he10_model <- he10(U=4,dt=1/365,Tmax=switch(i,1955,1964),
  expandedParNames=c("g"),
  towns_selected=c(1,2,11,12),
  basic_params = c(
    alpha =0.99,      iota=0,          R0=30,
    cohort=0.5,  amplitude=0.3,     gamma=52,
    sigma=52,           mu=0.02,  sigmaSE=0.05,
    rho=0.5,           psi=0.1,         g=800,
    S_0=0.036,         E_0=0.00007,   I_0=0.00006
  )
)
m_g <- simulate(he10_model,seed=27)
if(any(dim(obs(m_g))!=dim(obs(m_R0))) || any(obs(m_g)-obs(m_R0) != 0)) stop("m_g and m_R0 should have the same synthetic data")
})
@
